Quantifying the Impact \\ of Performance Improvements and Cost Reductions \\ from 20 years of Light-Emitting Diode Manufacturing

### 2021-02-06 SPIE/article/main.tex
added final figure

To quantify changes in the manufacturing cost of devices, a bottom-up manufacturing cost model with process step resolution was constructed to cover the entire manufacturing process of GaN-on-sapphire based phosphor converted low-to-mid power light-emitting diode packages of different chip architectures. We considered classical p-side-up lateral current spreading devices, as well as a packaged flip-chip vertical current spreading architecture and a chip-scale package flip chip architecture. The model was constructed for the years 2003, 2012 and 2020. It was populated with equipment data from European and North American firms, selected for a virtual North American manufacturing location. Process specific step parameters were derived from scientific literature, company publications, archived product catalogs and patent literature. Details of the manufacturing process, as well as changes in the same were gathered from detailed patent analysis, augmented by interviews with experts from industry and academia. For 2012, data for the model was adapted from the \textit{LEDCOM} cost model prepared for the US Department of Energy by Stephen Bland. The model includes both the wafer treatment process as well as the packaging process. It is important to note that the aim of the model is not to faithfully represent real world manufacturing conditions in Asia based plants, but rather to show the effect of single technological changes in the manufacturing process on total cost. This means that while the model does consider overhead costs and depreciation, it does so only to XXXX

@@

@@

\section{MANUFACTURING COST}

show two waterfall diagrams (2003 only). mention work in progress

>>>>

    \subsection{Manufacturing Cost Model}
To quantify changes in the manufacturing cost of devices, a bottom-up manufacturing cost model with process step resolution was constructed to cover the entire manufacturing process of GaN-on-sapphire based phosphor converted low-to-mid power light-emitting diode packages of different chip architectures. We considered classical p-side-up lateral current spreading devices, as well as a packaged flip-chip vertical current spreading architecture and a chip-scale package flip chip architecture. The model was constructed for the years 2003, 2012 and 2020. It was populated with equipment data from European and North American firms, selected for a virtual North American manufacturing location. Process specific step parameters were derived from scientific literature, company publications, archived product catalogs and patent literature. Details of the manufacturing process, as well as changes in the same were gathered from detailed patent analysis, augmented by interviews with experts from industry and academia. For 2012, data for the model was adapted from the \textit{LEDCOM} cost model prepared for the US Department of Energy by Stephen Bland. The model includes both the wafer treatment process as well as the packaging process. It is important to note that the aim of the model is not to faithfully represent real world manufacturing conditions in Asia based plants, but rather to show the effect of single technological changes in the manufacturing process on total cost. This means that while the model does consider overhead costs and depreciation, it does so only to XXXX

@@

        \subsection{Literature Review and Performance Computation}

@@

\section{MANUFACTURING COST REDUCTIONS}

\clearpage

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=0.85\textwidth]{SPIE/article/costmodel_calibration.pdf}
    \end{center}
    \caption{Modeled manufacturing cost for the specified architecture of light-emitting diode packages split by manufacturing step category, following the XXX in US DoE reports \cite{doe2016solid}. The top graph shows the data from \textit{LEDCOM} model and  round table discussions published by the United States Department of Energy. The bottom graph shows the results of the cost model developed in this thesis. Die per wafer calculated from de Vries \cite{deVries2005}}
    \label{fig:cost}
\end{figure}
